Wireless Automobile Detection, License Plate Processing, and Data Availability Network

### 2014-05-01 paper/paper.tex
Slight wording change in image processing methods

Two datasets are analyzed on how they ran through the OCR software (section 4.2). These two datasets, "cropped images" and "compressed images" had different methods of processing applied. "Cropped images" is a set of images that were greedily cropped to eliminate space at the top and bottom of the picture around the car and were converted to grayscale images. "Compressed images" is a set of images that had various amounts of compression applied to them as well as different color filters.

>>>>

Two datasets are analyzed on how they ran through the OCR software (section 4.2). These two datasets, "cropped images" and "compressed images" had different methods of processing applied. "Cropped images" is a set of images that were naively cropped to eliminate space at the top and bottom of the picture around the car and were converted to grayscale images. "Compressed images" is a set of images that had various amounts of compression applied to them as well as different color filters.
